---
#title: "distracted_driving_workflow"
output: html_document
---

```{r data, message=FALSE}
library(ggplot2)
library(magrittr)
library(dplyr)
library(rstan)

df_feather <- feather::read_feather(here::here("study_df", "df.feather"))
subject_bio <- feather::read_feather(here::here("study_df", "subject_bio.feather"))

df <- df_feather %>% 
    dplyr::select(Subject, Distance, Lane.Position, Drive, phase,
                  Gaze.X.Pos, Gaze.Y.Pos, Lft.Pupil.Diameter, Rt.Pupil.Diameter,
                  gender, age_group, tai, type_ab) %>%
    dplyr::mutate(age_group=as.factor(age_group))

nd_df <- df %>% dplyr::filter(Drive == "ND") 
md_df <- df %>% dplyr::filter(Drive == "MD") 
nd_nolanechange <- nd_df %>% dplyr::filter(!dplyr::between(Distance, 5000, 7000))
md_nolanechange <- md_df %>% dplyr::filter(!dplyr::between(Distance, 5000, 7000))
source(here::here('src', 'codebase', 'stan_utility.R'))
```

## Objective

- Determine how lane deviation volatility is affected by sensorimotor driving (MD), aka texting while driving, compared to normal driving (ND)
    - Phases proceeding stimulus

- Eye gazing / pupilation are explanatory variables to lane positioning / volatility

- Compare lane deviation volatility by cohorts (age, gender, psychometric survey)

```{r, warning=FALSE, fig.align="center", echo=FALSE}
ggplot(df, aes(x=Distance, y=Lane.Position)) +
    geom_line(aes(colour=phase)) +
    facet_grid(Drive ~ .) +
    theme_bw() +
    labs(x = 'Distance', y = 'Lane Position (m)') +
    theme(legend.position = "bottom")
```

## Model 1.0: First down

Trying to capture normal driving behavior without lane change and with age cohort

```{r}
ggplot(nd_nolanechange, aes(x=Distance, y=Lane.Position)) + 
    geom_line(aes(color=Subject)) +
    facet_grid(. ~ age_group)  +
    theme_bw() +
    labs(x = 'Distance', y = 'Lane Position (m)') +
    theme(legend.position = "none")
```

$$y_n(i) \sim \mathcal{N}(\mu_n, \sigma_n)$$

$$\mu_n\sim \mu_0+ \mu_{age} + \beta x_i$$

where $n \in \{ 1, \ldots, 68 \}$ and $i:$ Distance

### 1. Conceptual analysis

68 drivers from two different age groups and genders with pupil dilation recorded at each point in space (distance). Lane position is recorded at each point of distance and with likely little change in the normal driving scenario after not including the lane change.

### 2. Define Observations
```{r}
writeLines(readLines(here::here("src", "stan", "nd_no_lanechange.stan"), n=5))
```

### 3. Identify relevant summary statistics 

The standard deviation will be a useful summary statistic. Given the 4 lane highway, it would be possible but unlikely to see lane positions change by more than 4 meters, especially without a lane change. Might be able to see differences based on age.

```{r, echo=FALSE, message=FALSE}
library(dplyr)
library(purrr)

mean_lane <- function(df) mean(df$Lane.Position, na.rm=TRUE)
sd_lane <- function(df) sd(df$Lane.Position, na.rm=TRUE)

mean_leye <- function(df) sd(df$Rt.Pupil.Diameter, na.rm=TRUE)
mean_reye <- function(df) sd(df$Lft.Pupil.Diameter, na.rm=TRUE)

nd_nest <- nd_nolanechange %>% group_by(Subject) %>% tidyr::nest() %>%
    inner_join(subject_bio, by=c("Subject" = "subject")) %>%
    mutate(avg_lane=map_dbl(data, mean_lane), 
           sd_lane=map_dbl(data, sd_lane),
           r_dilation=map_dbl(data, mean_reye),
           l_dilation=map_dbl(data, mean_leye))
nd_nest %>% group_by(age_group) %>% summarize(mean(avg_lane), mean(sd_lane))
rm(mean_lane, mean_leye, mean_reye, sd_lane)
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

