---
title: "STAT 685: Distracted Driving"
subtitle: "Assignment 3"
author: "Bryan Yu: bryanyu@tamu.edu"
output: pdf_document
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
library(dplyr)
library(ggplot2)
library(rstan)
library(gridExtra)
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)

df <- feather::read_feather(here::here("study_df", "df.feather"))
df_select <- feather::read_feather(here::here("study_df", "df_select.feather"))
subject_df <- feather::read_feather(here::here("study_df", "subject_df.feather"))

nd_nolanechange <- df_select %>% dplyr::filter(Drive == "ND") %>% 
    dplyr::filter( !dplyr::between(Distance, 5000, 7000))
md_nolanechange <- df_select %>% dplyr::filter(Drive == "MD") %>% 
    dplyr::filter( !dplyr::between(Distance, 5000, 7000))

source(here::here("src", "codebase", "stan_utility.R"))
```

## Objective: 
Model volatility of lane positioning with regards to texting effect and population effects (age cohort)

## Summary

Focused this analysis on getting some linear regression models with multiple effects (age / texting) on aggregated data, sampled by each driver. Was able to create simulated and capture the effects within uncertainty parameters. However, was not able to meaningfully capture effects of age/texting with the actual data. May need to pool results in a hierarchical model to reduce uncertainty and observe effects of age/texting. Also need to perform posterior predictive checks.

*Future steps*

0. Handle '0' data on eye gaze more effectively

1. Pool effects for regularization to reduce uncertainty in the groups (age and texting)

2. Iterate on time series model with respect to stochastic volatilty model

* log volatility
* persistence of volatility
* log volatility at distance d

3. Change-point model (account for driving phases)

\newpage

## Data Analysis

```{r data_setup, echo=FALSE, cache=TRUE}
# Check how many variables are missing
data_check <- nd_nolanechange %>% 
    mutate(Rpupil=!is.nan(Rt.Pupil.Diameter) & Rt.Pupil.Diameter != 0,
           Lpupil=!is.nan(Lft.Pupil.Diameter) & Lft.Pupil.Diameter != 0,
           Ygaze=!is.nan(Gaze.Y.Pos) & Gaze.Y.Pos != 0,
           Xgaze=!is.nan(Gaze.X.Pos) & Gaze.X.Pos != 0) %>%
    group_by(Subject) %>%
    summarize(num_Rpupil=sum(Rpupil, na.rm=TRUE),
              num_Lpupil=sum(Lpupil, na.rm=TRUE),
              num_Ygaze=sum(Ygaze, na.rm=TRUE),
              num_XGaze=sum(Xgaze, na.rm=TRUE))


# aggregated data
gaze_nd <- nd_nolanechange %>%
    filter(Gaze.Y.Pos > 0) %>%
    group_by(Subject) %>%
    summarize(sd_lane_position=sd(Lane.Position, na.rm = TRUE),
              sd_log_lane_position=log(sd_lane_position),
              sd_y_gaze=sd(Gaze.Y.Pos),
              sd_log_y_gaze=log(sd(Gaze.Y.Pos))) %>%
    inner_join(subject_df, by=c("Subject"="subject")) %>% 
    select(Subject, 
           sd_lane_position, sd_log_lane_position,
           sd_y_gaze, sd_log_y_gaze, age_group) %>%
    mutate(texting=1)

gaze_md <- md_nolanechange %>%
    filter(Gaze.Y.Pos > 0) %>%
    group_by(Subject) %>%
    summarize(sd_lane_position=sd(Lane.Position, na.rm = TRUE),
              sd_log_lane_position=log(sd_lane_position),
              sd_y_gaze=sd(Gaze.Y.Pos + 0.01),
              sd_log_y_gaze=log(sd(Gaze.Y.Pos))) %>%
    inner_join(subject_df, by=c("Subject"="subject")) %>% 
    select(Subject, 
           sd_lane_position, sd_log_lane_position,
           sd_y_gaze, sd_log_y_gaze, age_group) %>%
    mutate(texting=2)

gaze <- gaze_nd %>% bind_rows(gaze_md) %>%
    mutate(age_group=as.factor(age_group), texting=as.factor(texting))
```

```{r fig.height=3, echo=FALSE}
# 0 data
par(mfrow=c(1, 2))
hist(nd_nolanechange$Gaze.Y.Pos, xlab="Gaze in Y", main="Normal driving")
hist(md_nolanechange$Gaze.Y.Pos, xlab="Gaze in Y", main="Texting driving")
par(mfrow=c(1, 1))
```

```{r plot, echo=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
library(gridExtra)
library(grid)

grid_arrange_shared_legend <- function(..., ncol = length(list(...)), nrow = 1, position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position="none"))
  gl <- c(gl, ncol = ncol, nrow = nrow)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = unit.c(unit(1, "npc") - lwidth, lwidth)))

  grid.newpage()
  grid.draw(combined)

  # return gtable invisibly
  invisible(combined)

}
sd_plot_nd <- ggplot(gaze_nd, aes(sd_y_gaze, sd_lane_position)) +
    geom_point(aes(colour=age_group)) +
    theme_bw() +
    labs(x = "Y-plane eye gaze std dev", y="Lane position std dev",
         title="ND: raw data", colour="Age Group") +
    coord_cartesian(xlim = c(0, 225), ylim=c(0, 0.7))

sd_log_plot_nd <- ggplot(gaze_nd, aes(sd_log_lane_position, sd_log_y_gaze)) +
    geom_point(aes(colour=age_group)) +
    theme_bw() +
    labs(x = "Y-plane eye gaze std dev", y="Lane position std dev",
         title="ND: Log transformed", colour = "Age Group") +
    coord_cartesian(xlim = c(-3, 0), ylim=c(3, 5.5))

sd_plot_md <- ggplot(gaze_md, aes(sd_y_gaze, sd_lane_position)) +
    geom_point(aes(colour=age_group)) +
    theme_bw() +
    labs(x = "Y-plane eye gaze std dev", y="Lane position std dev",
         title="MD: raw data", colour="Age Group") + 
    coord_cartesian(xlim = c(0, 225), ylim=c(0, 0.7))

sd_log_plot_md <- ggplot(gaze_md, aes(sd_log_lane_position, sd_log_y_gaze)) +
    geom_point(aes(colour=age_group)) +
    theme_bw() +
    labs(x = "Y-plane eye gaze std dev", y="Lane position std dev",
         title="MD: Log transformed", colour = "Age Group") +
    coord_cartesian(xlim = c(-3, 0), ylim=c(3, 5.5))

grid_arrange_shared_legend(sd_plot_nd, sd_log_plot_nd, sd_plot_md, sd_log_plot_md, ncol=2, nrow=2)
```

* Filtered out 0 data from eye gaze (this approximation may be too gross)
* Filtered out missing eye gaze data (will look at modelling this later)
* Log transformation of standard deviation data to unconstrain data for simplier model

\newpage

## Model 01: Simple linear regression for lane volatility

$y_n:$ Log std dev of lane position

$x_n:$ Log std dev of y-axis eye gaze

$\beta:$ Effect of std in eye gaze

$\alpha_0:$ Intercept of lane position

$\alpha_{age}$: Effect of age cohort

$\alpha_{texting}$: Effect of texting

### 1. Probability Model: Priors and likelihoods

**Homogeneous population:**

$$y_n \sim \mathcal{N}(\alpha_0 + \beta x_n, \sigma) $$


**Heterogeneous population:**

$$y_n \sim \mathcal{N}(\alpha_0 + \alpha_{age} + \beta x_n, \sigma) $$

**Heterogeneous with texting populations:**

$$y_n \sim \mathcal{N}(\alpha_0 + \alpha_{age} + \alpha_{texting} + \beta x_n, \sigma) $$

---

**Priors**

Empirical priors with wide band

$$\beta \sim \mathcal{N}(0, 5)$$

$$\alpha_0 \sim \mathcal{N}(1.825, 5)$$

$$\alpha_{age} \sim \mathcal{N}(0, 5)$$

$$\alpha_{texting} \sim \mathcal{N}(0, 5)$$

\newpage

### 2. Simulated data with known parameters


**Simulated model 1a: Homogeneous population (age)**

$n = 200$ for all simulations

```
transformed data {
  real alpha0 = 1.825;
  real beta = -2;
  real<lower=0> sigma = 0.5;
}
```

```{r sim_homo, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
load(here::here("sim_models.RData"))
la <- rstan::extract(fit_homo, permuted=TRUE)
```

**Simulated model 2b: Heterogeneous population (age)**

```
transformed data {
  real alpha0 = 1.825;
  int N_age = 2;
  vector[2] alpha_age = [0.25, -0.25]';
  real beta = -2;
  real<lower=0> sigma = 0.5;
}

```

```{r sim_hetero, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
lb <- rstan::extract(fit_hetero, permuted=TRUE)
```

**Simulated model 3b: Heterogeneous population (age) with texting**

```
transformed data {
  real alpha0 = 1.825;
  int N_age = 2;
  vector[2] alpha_age = [0.25, -0.25]';
  vector[2] alpha_texting = [0.5, -.5]';
  real beta = -2;
  real<lower=0> sigma = 0.5;
}
```

```{r sim_texting, message=FALSE, warning=FALSE, cache=TRUE, echo=FALSE}
lc <- rstan::extract(fit_texting, permuted=TRUE)
```

```{r generative_ensemble, cache=TRUE, echo=FALSE, fig.height=4}
par(mfrow=c(1, 3))
hist(la$log_y, main="Single age cohort", xlab="Log std dev")
hist(lb$log_y, main="Different ages", xlab="Log std dev")
hist(lc$log_y, main="Different ages + texting", xlab="Log std dev")
par(mfrow=c(1, 1))
```

### 3. Estimate model with simulated data

```{r results, cache=TRUE}
load(here::here("fitted_sim_models.RData"))
homo_model

hetero_model

texting_model
```

Models captured parameters within sd

\newpage

### 4. Estimate model with actual data

```{r}
load(here::here("fitted_act_models.RData"))

act_homo_model

act_hetero_model

act_texting_model

```

### 5. Model fit

Todo:

Posterior predictive checks 

### 6. Model comparison 

### 7. Inference

\newpage

## Model 02: Time series model:


```{r}
acf(nd_nolanechange$Lane.Position[nd_nolanechange$Subject=="T001"], main="")
```

